### 2018-06-15 Paper/abstract.tex
..

\section*{Abstract}
We develop a systematic approach for surrogate model
construction in reduced input parameter spaces.
%using derivative-based global sensitivity measures~(DGSMs)~\cite{Sobol:2010}. 
%
A sparse set of model evaluations in the original input space is used to  
approximate derivative based global sensitivity measures (DGSMs) 
for individual uncertain inputs of the model.
An iterative screening procedure is developed that exploits DGSM estimates in
order to identify the \emph{unimportant} inputs. The screening procedure forms
an integral part of an overall framework for adaptive construction of a
surrogate in the reduced space. The framework is tested for computational
efficiency through an initial implementation in simple test cases such as the
classic Borehole function, and a semilinear elliptic PDE with a random source
term. 
%Motivated by these experiences, the framework is fully implemented to
The framework is then deployed for a realistic application from chemical
kinetics, where we study the ignition delay time in an H$_2$/O$_2$ reaction
mechanism with 19 uncertain rate constants.  It is observed that significant
computational gains can be attained by constructing accurate low-dimensional
surrogates using the proposed framework.

>>>>

\section*{Abstract}
We develop a systematic approach for surrogate model
construction in reduced input parameter spaces.
%using derivative-based global sensitivity measures~(DGSMs)~\cite{Sobol:2010}. 
%
A sparse set of model evaluations in the original input space is used to  
approximate derivative based global sensitivity measures (DGSMs) 
for individual uncertain inputs of the model.
An iterative screening procedure is developed that exploits DGSM estimates in
order to identify the \emph{unimportant} inputs. The screening procedure forms
an integral part of an overall framework for adaptive construction of a
surrogate in the reduced space. The framework is tested for computational
efficiency through an initial implementation in simple test cases such as the
classic Borehole function, and a semilinear elliptic PDE with a random source
term. 
%Motivated by these experiences, the framework is fully implemented to
The framework is then deployed for a realistic application from chemical
kinetics, where we study the ignition delay in an H$_2$/O$_2$ reaction
mechanism with 19 uncertain rate constants.  It is observed that significant
computational gains can be attained by constructing accurate low-dimensional
surrogates using the proposed framework.

### 2018-06-15 Paper/app.tex
..

The reaction rate for the $i^{th}$ reaction as a function of temperature
is given as follows:
\be
k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT), 
\label{eq:rate}
\ee
%
where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$ is the
activation energy corresponding to the $i^{th}$ reaction, and $R$ is the
universal gas constant. 
The TChem~\cite{Safta:2011} software package is used to model homogenous
ignition at constant pressure for a range of initial conditions for the
fuel-oxidizer mixture. During the simulation, the fuel-oxidizer mixture goes 
through a radical build-up phase followed by a sharp increase in temperature
as heat is realeased during the thermal runaway. We focus on quantifying the 
uncertainty in the \emph{ignition delay} due to uncertainty associated 
with the pre-exponent, $A_i$, for each reaction. The ignition delay 
is defined as the inflection point on the temperature profile during the thermal
runaway. The total number of uncertain parameters in the
present case is 19.  The $A_i$'s are considered to be uniformly distributed in
the interval: $[0.9A_i^\ast, 1.1A_i^\ast]$; $A_i^\ast$ being the nominal
estimate corresponding to the $i^{th}$ reaction.
The set of nominal values used in the computations, for parameters 
in~\eqref{eq:rate} are provided
in~\cite{Yetter:1991}.

>>>>

The reaction rate for the $i^{th}$ reaction as a function of temperature
is given as follows:
\be
k_i(T) = A_iT^{n_i}\exp(-E_{a,i}/RT), 
\label{eq:rate}
\ee
%
where $A_i$ is the pre-exponent, $n_i$ is the index of $T$, $E_{a,i}$ is the
activation energy corresponding to the $i^{th}$ reaction, and $R$ is the
universal gas constant. 
The TChem~\cite{Safta:2011} software package is used to model homogeneous
ignition at constant pressure for a range of initial conditions for the
fuel-oxidizer mixture. During the simulation, the fuel-oxidizer mixture goes 
through a radical build-up phase followed by a sharp increase in temperature
as heat is released during the thermal runaway. We focus on quantifying the 
uncertainty in the \emph{ignition delay} due to uncertainty associated 
with the pre-exponent, $A_i$, for each reaction. The ignition delay 
is defined as the inflection point on the temperature profile during the thermal
runaway. The total number of uncertain parameters in the
present case is 19.  The $A_i$'s are considered to be uniformly distributed in
the interval: $[0.9A_i^\ast, 1.1A_i^\ast]$; $A_i^\ast$ being the nominal
estimate corresponding to the $i^{th}$ reaction.
The set of nominal values used in the computations, for parameters 
in~\eqref{eq:rate} are provided
in~\cite{Yetter:1991}.

### 2018-06-15 Paper/bg.tex
..

If an analytic expression for $\GG$ is available the derivative in the above
expression can be computed directly. In many applications, however, $\GG$ is
often defined in terms of a solution of a mathematical model.  In some cases,
one has access to appropriate adjoint solvers that enable efficient
adjoint-based gradient computations. This is discussed further below.  In the
present work, we consider a generic computational model and only assume that
the model output depends differentiably on the parameter $\bm{\theta}$. A
simple approach to computing the gradient is to use finite-differences: 
\be
\frac{\partial \GG(\bm{\theta})}{\partial \theta_i} 
\approx
\frac{\GG(\theta_1,\ldots,\theta_{i-1},
\theta_i+\Delta\theta_i,
\theta_{i+1},\ldots,\theta_d) - 
\GG(\bm{\theta})}{\Delta\theta_i}, \quad i = 1, \ldots, \Np. 
\label{eq:partial}
\ee
Then,~\eqref{eq:mu} can be evaluated by Monte Carlo sampling in
the uncertain parameter space. 
The total number of model realizations or function evaluations
needed to
compute $\mu_i$ for a function $G$ of $\Np$ random inputs and using $N$ samples is
therefore, $N\times(\Np+1)$. 
%The derivative in Eq.~\ref{eq:partial} could be evaluated
%analytically in case the functional dependence of $\GG$ and $\theta_i$
%is known. 
%Note that the perturbation $\Delta\theta_i^{*}$ is extremely small 
%compared to the uncertainty in $\theta_i$ which leads to a significant improvement
%over the `elementary effect' of a parameter, estimated in the Morris method~\cite{Morris:1991}
%using large increments.  
It is noted by many authors~\alennote{Need to give some references}, and also
observed in the numerical experiments in the present work, that a modest Monte
Carlo sample size is often sufficient for computing~\eqref{eq:mu} with
sufficient accuracy to indentify the unimportant inputs.

Consider the total 
Sobol' sensitivity index~\cite{Sobol:2001},
\be
\mathcal{T}(\theta_i) = 1 - 
\frac{\mathbb{V}[\mathbb{E}(\GG|\bm{\theta}_{\sim i})]}{\mathbb{V}(\GG)},
\label{eq:total}
\ee
where $\bm{\theta}_{\sim i}$ is the random vector $\bm\theta$ with $i$th component removed, 
and $\mathbb{V}$ denotes the variance. The total Sobol' index quantifies the total contribution 
of $\theta_i$ to variance of the model $\GG$. Components of $\bm\theta$ with small 
total Sobol' index can be considered inessential and can be fixed at nominal values. However, 
computing the total Sobol' index is a computationally expensive task for expensive-to-evaluate 
models with large number of uncertain parameters. Fortunately, 
for parameters with continuous distributions, an upper bound on $\mathcal{T}_i$  
can be expressed in terms of $\mu_i$ as follows: 
\be
\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{\mathbb{V}(\GG)},
%~(\propto \widehat{\mathcal{C}_i\mu_i})
\label{eq:bound}
\ee
where $\mathcal{C}_i$ is the corresponding ``Poincar\'e constant''
and
$\mathbb{V}(\GG)$ is the total variance of the model
output~\cite{Lamboni:2013}.  The upper bound in the above inequality is
proportional to the product of $\mathcal{C}_i$ and $\mu_i$.  For the purpose of
parameter screening as discussed later in Section~\ref{sec:method}, we consider
a normalized product, $\widehat{\mathcal{C}_i\mu_i}$ to ensure that it lies
between 0 and 1:
\be
\widehat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}
\label{eq:cmu}
\ee
The Poincar\'e constant, $\mathcal{C}_i$ is specific to the probability
distribution of $\theta_i$. For $\theta_i \sim \mathcal{U}[a, b]$,
$\mathcal{C}_i = (b-a)^{2}/\pi^2$, and for  
$\theta_i \sim \mathcal{N}(\mu,\sigma^2)$, we have $\mathcal{C}_i = \sigma^2$. 
Here $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with mean $\mu$
and variance $\sigma^2$, and $\mathcal{U}[a,b]$ denotes a uniform distribution
on the interval $[a, b]$.

@@

\be
\hat{\bm{c}} = \mbox{argmin}~\mathbb{E}_{\bm\theta}
\left[\left(\sum_{k=0}^\Npc c_k \Psi_k(\bm\xi(\bm\theta)) -
\GG(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}}
\label{eq:reg}
\ee
where $\normone{\bm{c}}$ = $\sum_{k=0}^\Npc |c_k |$.
The regularization term forces the minimization towards sparse coefficient vectors resulting
in sparse PC representations.
In this work, we construct sparse PCEs with LAR using UQLab~\cite{Marelli:2014},
a general purpose uncertainty quantification software developed at ETH Zurich.
% in Switzerland.

>>>>

If an analytic expression for $\GG$ is available the derivative in the above
expression can be computed directly. In many applications, however, $\GG$ is
often defined in terms of a solution of a mathematical model.  In the
present work, we consider a generic computational model and only assume that
the model output depends differentiably on the parameter $\bm{\theta}$. A
simple approach to computing the gradient is to use finite-differences: 
\be
\frac{\partial \GG(\bm{\theta})}{\partial \theta_i} 
\approx
\frac{\GG(\theta_1,\ldots,\theta_{i-1},
\theta_i+\Delta\theta_i,
\theta_{i+1},\ldots,\theta_d) - 
\GG(\bm{\theta})}{\Delta\theta_i}, \quad i = 1, \ldots, \Np. 
\label{eq:partial}
\ee
Then,~\eqref{eq:mu} can be evaluated by Monte Carlo (MC) sampling in
the uncertain parameter space. 
The total number of model realizations or function evaluations
needed to
compute $\mu_i$ for a function $G$ of $\Np$ random inputs and using $N$ samples is
therefore, $N\times(\Np+1)$. 
%The derivative in Eq.~\ref{eq:partial} could be evaluated
%analytically in case the functional dependence of $\GG$ and $\theta_i$
%is known. 
%Note that the perturbation $\Delta\theta_i^{*}$ is extremely small 
%compared to the uncertainty in $\theta_i$ which leads to a significant improvement
%over the `elementary effect' of a parameter, estimated in the Morris method~\cite{Morris:1991}
%using large increments.  
It is noted in previous studies~\cite{Kucherenko:2016,Kucherenko:2009},
and also
observed in the numerical experiments in the present work, that a modest MC sample size is often sufficient for computing~\eqref{eq:mu} with
reasonable accuracy to indentify the unimportant inputs. Moreover, the
computational efficiency for estimating $\mu_i$ can be enhanced by using
techniques such as the automatic differentiation
algorithm~\cite{Kiparissides:2009}.

Consider the total 
Sobol' sensitivity index~\cite{Sobol:2001},
\be
\mathcal{T}(\theta_i) = 1 - 
\frac{\mathbb{V}[\mathbb{E}(\GG|\bm{\theta}_{\sim i})]}{\mathbb{V}(\GG)},
\label{eq:total}
\ee
where $\bm{\theta}_{\sim i}$ is the random vector $\bm\theta$ with $i$th component removed, 
and $\mathbb{V}$ denotes the variance. The total Sobol' index quantifies the total contribution 
of $\theta_i$ to variance of the model $\GG$. Components of $\bm\theta$ with small 
total Sobol' index can be considered inessential and can be fixed at nominal values. However, 
computing the total Sobol' index is a computationally expensive task for expensive-to-evaluate 
models with large number of uncertain parameters. Fortunately, 
for parameters with continuous distributions, an upper bound on $\mathcal{T}_i$  
can be expressed in terms of $\mu_i$ as follows: 
\be
\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{\mathbb{V}(\GG)},
%~(\propto \widehat{\mathcal{C}_i\mu_i})
\label{eq:bound}
\ee
where $\mathcal{C}_i$ is the corresponding ``Poincar\'e constant''
and
$\mathbb{V}(\GG)$ is the total variance of the model
output~\cite{Lamboni:2013}.  The upper bound in the above inequality is
proportional to the product of $\mathcal{C}_i$ and $\mu_i$.  For the purpose of
parameter screening as discussed later in Section~\ref{sec:method}, we consider
a normalized product, $\widehat{\mathcal{C}_i\mu_i}$ to ensure that it lies
between 0 and 1:
\be
\widehat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}.
\label{eq:cmu}
\ee
The Poincar\'e constant, $\mathcal{C}_i$ is specific to the probability
distribution of $\theta_i$. For $\theta_i \sim \mathcal{U}[a, b]$,
$\mathcal{C}_i = (b-a)^{2}/\pi^2$, and for  
$\theta_i \sim \mathcal{N}(\mu,\sigma^2)$, we have $\mathcal{C}_i = \sigma^2$. 
Here $\mathcal{N}(\mu,\sigma^2)$ denotes a normal distribution with mean $\mu$
and variance $\sigma^2$, and $\mathcal{U}[a,b]$ denotes a uniform distribution
on the interval $[a, b]$.

@@

\be
\hat{\bm{c}} = \mbox{argmin}~\mathbb{E}_{\bm\theta}
\left[\left(\sum_{k=0}^\Npc c_k \Psi_k(\bm\xi(\bm\theta)) -
\GG(\bm{\theta})\right)^{2}\right]  + \lambda\normone{\bm{c}},
\label{eq:reg}
\ee
where $\normone{\bm{c}}$ = $\sum_{k=0}^\Npc |c_k |$.
The regularization term forces the minimization towards sparse coefficient vectors resulting
in sparse PC representations.
In this work, we construct sparse PCEs with LAR using UQLab~\cite{Marelli:2014},
a general purpose uncertainty quantification software developed at ETH Zurich.
% in Switzerland.

### 2018-06-15 Paper/disc.tex
..

In this work, we have presented a systematic and efficient approach for constructing
a reduced-space
surrogate for scientific and engineering applications. Dimension reduction is accomplished
by identifying uncertain parameters that contribute relatively less towards the uncertainty
in the quantity of interest. These parameters deemed as \textit{unimportant} are determined
using a screening metric~(\eqref{eq:cmu}) involving derivative-based sensitivity
measures. Initially, the metric is estimated
using model evaluations at a small set of samples in the parameter domain. However, these
estimates are refined by subsequent enrichment of the sample set during the screening
procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
assessed for the scope of dimension reduction. In a favorable scenario, a reduced-space
surrogate (RSS) is constructed. The RSS is tested for accuracy in a least-squares sense
as well as a probabilistic sense using a cross-validation test suite. In the proposed framework,
a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
the available set of model evaluations. Both, RSS and FSS are
constructed using regression-based sparse basis methods. Simultaneous construction
of the FSS ensures that the computational effort associated with the proposed framework
does not overshoot the effort required to construct the FSS directly.
Hence, the RSS is constructed only in situations where computational gains are
expected.

Parameter screening methodology was implemented to low-to-moderate dimensional
test problems and an accurate RSS was constructed to demonstrate potential for
computational gains in each case. Furthermore, the overall framework was
implemented  to a relatively higher dimensional application involving kinetics
of the H$_2$/O$_2$ reaction mechanism.  Significant dimension reduction (19 
dimensions to 3 or 4 dimensions) was
accomplished for two different scenarios involving a fuel-rich and a fuel-lean
mixture. In both cases, the resulting RSS was able to capture the input-output
relationship as well as the uncertainty in the quantity of interest with
reasonable accuracy. Additional highlights of the proposed framework are as
follows:
\begin{enumerate}
\item The proposed framework is agnostic to the choice of the surrogate although PCE's were used
in this work. 
\item The scope for dimension reduction and associated computational gains are
dependent upon the application as well as the quantity of interest. 
%\item The quantity of interest must be differentiable with respect to each uncertain parameter
%for the derivative-based sensitivity measures in~\eqref{eq:mu} to be defined. 
%to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
\item Substantial computational gains are expected in situations involving
compute-intensive simulations even if the scope for dimension reduction is
small. 
%Hence, careful judgment pertaining to the construction of a reduced-order
%surrogate as well as resource allocation is needed. is required when
%implementing the framework.

@@

Based on the results presented for a variety of test problems, and a
higher-dimensional chemical kinetics application in this work, it can be said
that the proposed framework seems quite promising in its potential for
identifying favorable scenarios for constructing a reduced-space surrogate in a
computationally efficient manner.  However, it is important to remain cognizant
about the limitations of the framework as well. For instance, it does not
account for the existence of possible correlations between the uncertain
inputs of the model. However, while the assumption of independent
inputs is not always justified, in many cases, correlations between
inputs are not well understood a priori, and assuming mutual independence
could be reasonable at least in initial screening using DGSMs. On the other
hand, if approximate correlations are known, we recommend using a Gaussian 
process or Kriging-based surrogate since it 
provides a means for incorporating the correlation between inputs.  
Additionally, the quantity of interest is required to be differentiable with
respect to each parameter in the considered domain. This condition, however,
must anyways be satisfied for the resulting surrogate to be able to represent
the input-output relationship for a given model with reasonable accuracy.
Finally, careful assessment and decision-making is required with regards to
proceeding with the construction of a reduced-space surrogate based on the
outcome of parameter screening, and accuracy of the most recent full-space
surrogate as well as allocation of computational resources for parameter
screening, and constructing the validation test suite. Implementation to more
advanced applications in the future would enable further development of the
proposed framework.

>>>>

In this work, we have presented an efficient and practical approach for constructing
a reduced-space
surrogate for scientific and engineering applications. Dimension reduction is accomplished
by identifying uncertain parameters that contribute relatively less towards the uncertainty
in the quantity of interest. These parameters deemed as \textit{unimportant} are determined
using a screening metric~\eqref{eq:cmu} involving derivative-based sensitivity
measures. Initially, the metric is estimated
using model evaluations at a small set of samples in the parameter domain. However, these
estimates are refined by subsequent enrichment of the sample set during the screening
procedure presented in Algorithm~\ref{alg:screen}. The outcome of parameter screening is
assessed for the scope of dimension reduction. In a favorable scenario, a reduced-space
surrogate (RSS) is constructed. The RSS is tested for accuracy in a least-squares sense
as well as a probabilistic sense using a cross-validation test suite. In the proposed framework,
a surrogate in the full-space (FSS) is constructed in tandem with parameter screening using
the available set of model evaluations. Both, RSS and FSS are
constructed using regression-based sparse PCEs. Simultaneous construction
of the FSS ensures that the computational effort associated with the proposed framework
does not overshoot the effort required to construct the FSS directly.
Hence, the RSS is constructed only in situations where computational gains are
expected.

Parameter screening methodology was implemented to low-to-moderate dimensional
test problems and an accurate RSS was constructed to demonstrate potential for
computational gains in each case. Furthermore, the overall framework was
implemented  to a relatively higher dimensional application involving kinetics
of the H$_2$/O$_2$ reaction mechanism.  Significant dimension reduction (19 
dimensions to 3 or 4 dimensions) was
accomplished for two different scenarios involving a fuel-rich and a fuel-lean
mixture. In both cases, the resulting RSS was able to capture the input-output
relationship as well as the uncertainty in the quantity of interest with
reasonable accuracy. Additional highlights of the proposed framework are as
follows:
\begin{enumerate}
\item Although PCEs were used in this work, the proposed framework is
agnostic to the choice of the surrogate model construction method.
%\item The quantity of interest must be differentiable with respect to each uncertain parameter
%for the derivative-based sensitivity measures in~\eqref{eq:mu} to be defined. 
%to ensure accurate estimation of the derivative-based sensitivity measures in~\eqref{eq:mu}.
\item Substantial computational gains are expected in situations involving
compute-intensive simulations even if the scope for dimension reduction is
small. 
%Hence, careful judgment pertaining to the construction of a reduced-order
%surrogate as well as resource allocation is needed. is required when
%implementing the framework.

@@

Based on the results presented for the test problems and the kinetics
application, the proposed framework seems quite promising in its
potential for identifying the unimportant model inputs. These
observations could be exploited to construct efficient model surrogates
in a reduced input space. However, it is important to remain cognizant
about the limitations of the framework as well. 
For instance, the quantity of interest is required to be differentiable with
respect to each parameter in the considered domain. This condition once
satisfied, helps improve the DGSM estimates and enhances the accuracy
of the PCE-based surrogates as well.  
Additionally, the proposed framework does not
account for the existence of possible correlations between the uncertain
inputs of the model. However, while the assumption of independent
inputs is not always justified, in many cases, correlations between
inputs are not well understood a priori, and assuming mutual independence
could be reasonable at least in initial screening using DGSMs. On the other
hand, if approximate correlations are known, we recommend using a Gaussian 
process or Kriging-based surrogate since it 
provides a means for incorporating the correlation between inputs.  
Implementation to applications involving strongly correlated parameters
could enhance the applicability of the proposed framework. 
We consider that to be a potential direction for future studies related
to this work.

### 2018-06-15 Paper/examples.tex
..

%
Cheap function evaluations of the discharge $\mathcal{Q}(\vec{\theta})$ using
enables computing accurate estimates of $\mathcal{T}(\theta_i)$ through
sampling, with a sufficiently large Monte Carlo sample size.  Shown in
Figure~\ref{fig:sense_bore}~(left) are estimates of these indices corresponding to the
uncertain parameters in the borehole function using 10$^6$ pseudo-random
samples in the input parameter space. 
%\footnote{Although $\mathcal{T}(\theta_i)$ might converge with much fewer
%samples depending upon the model, we consider a large number that typically
%ensures a converged estimate for the purpose of illustration.} 
These estimates are used to verify fidelity of
parameter screening based on the methodology presented in Section~\ref{sec:method}.

@@

Once again, we verify the accuracy of the RSS by estimating $\epsilon_{\mbox{\tiny{L-2}}}$
using model evaluations at 1000 independent Monte-Carlo samples in the 10D parameter
space. The RSS was found to be accurate
within 5$\%$. In order to bolster confidence in the RSS, we compare PDFs of the QoI
as well as a normalized histogram plot based on sparse model evaluations in the  
validation test-suite, in 
Figure~\ref{fig:conv_elliptic}~(right). While the two PDFs are in favorable agreement,
the modal estimate and the spread in the QoI based on the histogram is also captured
by them. Hence, the RSS could be used with a reasonable degree of confidence to
quantify the uncertainty in $\mathcal{F}(\kappa, c, \theta)$ thereby leading to
a computational advantage in this case.

>>>>

%
Cheap function evaluations of the discharge $\mathcal{Q}(\vec{\theta})$ using
enables computing accurate estimates of $\mathcal{T}(\theta_i)$ through
sampling, with a sufficiently large MC sample size.  Shown in
Figure~\ref{fig:sense_bore}~(left) are estimates of these indices corresponding to the
uncertain parameters in the borehole function using 10$^6$ pseudo-random
samples in the input parameter space. 
%\footnote{Although $\mathcal{T}(\theta_i)$ might converge with much fewer
%samples depending upon the model, we consider a large number that typically
%ensures a converged estimate for the purpose of illustration.} 
These estimates are used to verify fidelity of
parameter screening based on the methodology presented in Section~\ref{sec:method}.

@@

Once again, we verify the accuracy of the RSS by estimating $\epsilon_{\mbox{\tiny{L-2}}}$
using model evaluations at 1000 independent MC samples in the 10D parameter
space. The RSS was found to be accurate
within 5$\%$. In order to bolster confidence in the RSS, we compare PDFs of the QoI
as well as a normalized histogram plot based on sparse model evaluations in the  
validation test-suite, in 
Figure~\ref{fig:conv_elliptic}~(right). While the two PDFs are in favorable agreement,
the modal estimate and the spread in the QoI based on the histogram is also captured
by them. Hence, the RSS could be used with a reasonable degree of confidence to
quantify the uncertainty in $\mathcal{F}(\kappa, c, \theta)$ thereby leading to
a computational advantage in this case.

### 2018-06-15 Paper/intro.tex
..

Commonly used surrogate modeling approaches use polynomial chaos expansions
(PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate adaptive
regression splines (MARS)~\cite{friedman93}, Gaussian processes
(GPs)~\cite{Rasmussen:2004}, or kriging~\cite{Stein:2012}.  Many real-world
applications involve a large number of model inputs. This makes
the construction of surrogate models difficult or impossible in some cases.
However, in many situations, the variability in model observables of interest
is sensitive to only a small subset of the uncertain inputs.  Hence,
identifying model inputs that are inessential to variability in model output is
a key step that can help reduce the input parameter dimension and hence the effort
associated with surrogate model construction.

@@

\paragraph{Contributions}
The contributions of this article are as follows: (i) We establish a robust and
practical framework for dimension reduction in surrogate modeling using
derivate-based global sensitivity measures. Our
approach is general in that it is applicable to a wide range of applications.
(ii) We present comprehensive numerical results demonstrating the viability of
our strategy using motivating applications: the classic borehole
function, and a semilinear elliptic PDE.  (iii) We 
deploy our strategy in an application problem from chemical kinetics with 19
uncertain parameters. The problem is studied in multiple regimes.
It is shown that the 19-parameter problem can be efficiently reduced to a 3- 
or 4-dimensional problem.

>>>>

Commonly used surrogate modeling approaches use polynomial chaos expansions
(PCEs)~\cite{Xiu:2002,Ghanem:2003,Olivier:2010}, multivariate adaptive
regression splines (MARS)~\cite{friedman93}, Gaussian processes
(GPs)~\cite{Rasmussen:2004}, or Kriging~\cite{Stein:2012}.  Many real-world
applications involve a large number of model inputs. This makes
the construction of surrogate models difficult or impossible in some cases.
However, in many situations, the variability in model observables of interest
is sensitive to only a small subset of the uncertain inputs.  Hence,
identifying model inputs that are inessential to variability in model output is
a key step that can help reduce the input parameter dimension and hence the effort
associated with surrogate model construction.

@@

\paragraph{Contributions}
The contributions of this article are as follows: (i) We establish a robust and
practical framework for dimension reduction in surrogate modeling using
derivative-based global sensitivity measures. Our
approach is general in that it is applicable to a wide range of applications.
(ii) We present comprehensive numerical results demonstrating the viability of
our strategy using motivating applications: the classic borehole
function, and a semilinear elliptic PDE.  (iii) We 
deploy our strategy in an application problem from chemical kinetics with 19
uncertain parameters. The problem is studied in multiple regimes.
It is shown that the 19-parameter problem can be efficiently reduced to a 3- 
or 4-dimensional problem.
